---
title: "Development"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(delphidocs)
```

## Some notes for adjusting various components

You should be able to adjust `yml` variables controlling the styles. These are 
listed is the [bslib/_variables.scss](https://github.com/rstudio/bslib/blob/112efd0/inst/lib/bs5/scss/_variables.scss#L1195).

Other potentially useful resources:

* The [tidyverse template](https://github.com/tidyverse/tidytemplate/blob/main/inst/pkgdown/BS5/_pkgdown.yml)
* The [hubStyle template](https://github.com/hubverse-org/hubStyle/blob/main/inst/pkgdown/_pkgdown.yml)
* The [rOpenSci template](https://github.com/ropensci-org/rotemplate/blob/main/inst/pkgdown/_pkgdown.yml), especially the footer.

## When developing

To test features using this repository, I typically have to 
install the package first before rebuilding the site locally. So
you would iterate:

1. `devtools::install()`
2. `pkgdown::build_site()`
